---
title: "Cabbages"
author: "Christina maayah"
date: "Fall 2020"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->


 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$: the null hypothesis is that There is no difference in VitC content due to cultivation.

$H_A$: the alternative hypothesis is that There is a difference in VitC content due to cultivation.


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(VitC~Cult,data=veggy)
```


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(VitC~Cult,data=veggy)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The disparity in VitC content, according to the plot package, is that C52 has a higher content than C39 when using cultivation methods.
The numerical review indicates that C52 has about 13 units more than C39 using the method of culture. Finally, according to the t-test, 0.00000003 is less than 0.05, making it unlikely the null hypothesis; this means that it is likely to be the alternative and we deny the null hypothesis! Finally, we found a difference in the substance from the cultivation method in vitamins C39 and C52. According to the box plot the difference in VitC content is that when it is used, C52 is higher than C39. The numerical review indicates that C52 has about 13 units more than C39 using the method of culture. Finally, according to the t-test, 0.00000003 is less than 0.05, making it unlikely the null hypothesis; this means that it is likely to be the alternative and we deny the null hypothesis! Finally. 
